quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-04-05 paper-quollr.Rmd
Deleted unnecessary scripts

trimesh_removed_limb <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled,
    aes(
      x = emb1,
      y = emb2
    ),
    alpha = 0.3,
    color = "#a65628"
  ) +
    geom_segment(data = tr_from_to_df_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  #scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("b1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```

>>>>

trimesh_removed_limb <- ggplot() + 
  geom_point(
    data = tsne_limb_scaled,
    aes(
      x = emb1,
      y = emb2
    ),
    alpha = 0.3,
    color = "#a65628"
  ) +
    geom_segment(data = tr_from_to_df_limb, 
               aes(
                 x = x_from, 
                 y = y_from, 
                 xend = x_to, 
                 yend = y_to),
               colour = "#000000",
               linewidth = 1) +
  #scale_color_manual(values = c("#8dd3c7", "#fdb462", "#bebada")) +
  interior_annotation("a1", cex = 2) +
  theme(
    aspect.ratio = 1
  )
```
